---
title: "Exploratory Data Analysis"
author: "Meghana, Kowshik"
date: "`r Sys.Date()`"
output:  
   rmdformats::readthedown:
     highlight: kate
     code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scipen = 999)
library(ezids)
library(ggplot2)
```

```{r, results='markup'}
music = data.frame(read.csv("music_genre.csv"))
head(music)
```

```{r, results='markup'}
colnames(music)
```

```{r, results='markup'}
str(music)
```
# Changing vectors
Declaring key, mode, music_genre, tempo as categorical variables
```{r}
# changing vectors
music$key <- factor(music$key)
music$mode <- factor(music$mode)
music$music_genre <- factor(music$music_genre)
music$tempo <- as.numeric(music$tempo)
```

# checking and removing null values
```{r, results='hold'}
# checking and removing null values
paste0("Before removing missing values:", nrow(music))
print(colSums(is.na(music)))
music = na.omit(music)
paste0("After removing missing values:", nrow(music))
```

# Numerical features
```{r, results='markup'}
#seperating numeric values
numcolumns <- unlist(lapply(music,is.numeric))
music_cor <- music[,numcolumns]
music_cor <- music_cor[,-c(1)]

xkablesummary(music_cor)
```

# Correlations
```{r, results='markup'}
loadPkg("corrplot")
corrplot(cor(music_cor, method = "spearman"), method = "circle", type = 'lower', order = 'hclust', tl.col = 'black',
         cl.ratio = 0.1, tl.srt = 45, col = COL2('PuOr', 20))
```

# Plots
## Histograms
```{r, results='hold'}
# Histograms for all numeric columns
par(mfrow=c(2,3))
for (i in 1:ncol(music_cor[,1: ncol(music_cor)]))
{  
hist(music_cor[, i], breaks = 20, main = names(music_cor[i]), col = COL2('PuOr', 20), xlab = "")
}
```

## qqplots
```{r, results='hold'}
#qqplots for all numeric columns
par(mfrow=c(2,3))
for (i in 1:ncol(music_cor[,1: ncol(music_cor)]))
{  
qqnorm(music_cor[, i], main = names(music_cor[i]), pch = 18, col = "purple4")
   qqline(music_cor[, i], col = "orange")
}
```

## boxplots
```{r, results='hold'}
# boxplot for all numeric columns
par(mfrow=c(2,3))
for (i in 1:ncol(music_cor[,1: ncol(music_cor)]))
{  
boxplot(music_cor[, i],  main = names(music_cor[i]), col = "purple4", xlab = "")
}

```

# Removing outliers

```{r, results='hide'}
music2 <- data.frame(music)

# changing vectors
music2$key <- factor(music2$key)
music2$mode <- factor(music2$mode)
music2$music_genre <- factor(music2$music_genre)
music2$tempo <- as.numeric(music2$tempo)

# Removing outliers
music2 = outlierKD2(music2, popularity, rm = TRUE, histogram = FALSE)
music2 = outlierKD2(music2, danceability, rm = TRUE, histogram = FALSE)
music2 = outlierKD2(music2, loudness, rm = TRUE, histogram = FALSE)
music2 = outlierKD2(music2, liveness, rm = TRUE, histogram = FALSE)
music2 = outlierKD2(music2, duration_ms, rm = TRUE, histogram = FALSE)
music2 = outlierKD2(music2, speechiness, rm = TRUE, histogram = FALSE)
music2 = outlierKD2(music2, tempo, rm = TRUE, histogram = FALSE)

# Seperating numeric values
numcolumns2 <- unlist(lapply(music2,is.numeric))
music_cor2 <- music2[,numcolumns2]
music_cor2 <- music_cor2[,-c(1)]
```

```{r, results='hold'}
print("16210 out of 45020 rows were effected")
xkabledply(head(music2), title = "Dataframe without outliers")

```
# Plots after removing outliers

## Histogram
```{r, results='markup'}
# Histograms for all numeric columns
par(mfrow=c(2,3))
for (i in 1:ncol(music_cor2[,1: ncol(music_cor2)]))
{  
hist(music_cor2[, i], breaks = 20, main = names(music_cor2[i]), col = COL2('PuOr', 20), xlab = "")
}

```

## qqplot
```{r, results='markup'}
# qqplots for all numerical columns
par(mfrow=c(2,3))
for (i in 1:ncol(music_cor2[,1: ncol(music_cor2)]))
{  
qqnorm(music_cor2[, i], main = names(music_cor2[i]), pch = 18, col = "purple4")
   qqline(music_cor2[, i], col = "red")
}

```

## Boxplot
```{r, results='markup'}
# boxplots for all numeric columns
par(mfrow=c(2,3))
for (i in 1:ncol(music_cor2[,1: ncol(music_cor2)]))
{  
boxplot(music_cor2[, i], main = names(music_cor2[i]), col = "purple4", xlab = "")
}

```


## Genres
```{r, results='markup'}
unique(music$music_genre)
```

## Count
```{r, results='markup'}
# Genre frequency
music$music_genre <- factor(music$music_genre)
genre_count <- table(music$music_genre)
b <- barplot(genre_count, cex.names=0.7, col = COL2('PuOr', 10), ylim = c(0,5000), xlab = "Genre", ylab = "Count")
text(b, genre_count/2, genre_count, font = 2, col = "dark gray") 
```

## Average of each feature
```{r, results='markup'}
library(dplyr)
genres = music %>% group_by(music_genre)  %>%
                    summarise(popularity = mean(popularity),
                              acousticness = mean(acousticness),
                              danceability = mean(danceability),
                              duration_ms = mean(duration_ms),
                              energy = mean(energy),
                              instrumentalness = mean(instrumentalness),
                              liveness = mean(liveness),
                              loudness = mean(loudness),
                              speechiness = mean(speechiness),
                              tempo = mean(tempo),
                              valence = mean(valence))
 
xkabledply(genres, title = "Averages for each genre")
```

# Barplot to see energy of each music_genre
```{r, results='markup'}
library(ggplot2)
ggplot(data=music, aes(x=music_genre, y=energy)) +  
  geom_col(fill = "#00AFBB") + 
   labs(title='Energy of each music_genre', x="music_genre", y = "energy") + 
    theme(plot.title = element_text(hjust = 0.5))
```

# Barplot to see popularity of each Music Genre by energy wise
```{r, results='markup'}
library(ggplot2)
ggplot(data=music, aes(x=music_genre, y=popularity)) +  
  geom_col(fill = "#00AFBB") + 
   labs(title='Energy of each music_genre', x="music_genre", y = "popularity") +             theme(plot.title = element_text(hjust = 0.5))
```

## Distribution of each feature
```{r, results='hold'}
library(patchwork)
d1 <- ggplot(music, aes(x = popularity, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='Popularity', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d2 <- ggplot(music, aes(x = acousticness, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='acousticness', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d3 <- ggplot(music, aes(x = danceability, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='danceability', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d4 <- ggplot(music, aes(x = duration_ms, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='duration_ms', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d5 <- ggplot(music, aes(x = energy, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='energy', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d6 <- ggplot(music, aes(x = instrumentalness, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='instrumentalness', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d7 <- ggplot(music, aes(x = liveness, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='liveness', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d8 <- ggplot(music, aes(x = loudness, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='loudness', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d9 <- ggplot(music, aes(x = speechiness, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='speechiness', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d10 <- ggplot(music, aes(x = tempo, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='tempo', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d11 <- ggplot(music, aes(x = valence, col = music_genre)) +    
  geom_density(size = 1) +
  labs(title='valence', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position= "none") +
  scale_color_brewer(palette = "PuOr")

d1 + d2 + d3 + d4 + d5 + d6
d7 + d8 + d9 + d10 + d11

```

## Average of features for each genre
```{r, results='hold'}
#install.packages("patchwork")
library(patchwork)
p1 <- ggplot(genres, aes(music_genre, popularity, fill = music_genre)) +    
  geom_bar(stat = "identity") +
  labs(title='Average popularity', x = "Genre") +
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p2 <- ggplot(genres, aes(music_genre, acousticness, fill = music_genre)) +    
  geom_bar(stat = "identity") +
   labs(title='Average acoustiness', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p3 <- ggplot(genres, aes(music_genre, danceability, fill = music_genre)) +     
  geom_bar(stat = "identity") +
   labs(title='Average danceability', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p4 <- ggplot(genres, aes(music_genre, duration_ms, fill = music_genre)) +     
  geom_bar(stat = "identity") +
   labs(title='Average duration', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p5 <- ggplot(genres, aes(music_genre, energy, fill = music_genre)) +     
  geom_bar(stat = "identity") +
   labs(title='Average energy', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p6 <- ggplot(genres, aes(music_genre, instrumentalness, fill = music_genre)) +     
  geom_bar(stat = "identity") +
   labs(title='Average instrumentalness', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p7 <- ggplot(genres, aes(music_genre, liveness, fill = music_genre)) +     
  geom_bar(stat = "identity") +
   labs(title='Average liveness', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p8 <- ggplot(genres, aes(music_genre, loudness, fill = music_genre)) +     
  geom_bar(stat = "identity") +  scale_y_reverse() +
   labs(title='Average loudness', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p9 <- ggplot(genres, aes(music_genre, speechiness, fill = music_genre)) +     
  geom_bar(stat = "identity") +
   labs(title='Average speechiness', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p10 <- ggplot(genres, aes(music_genre, tempo, fill = music_genre)) +     
  geom_bar(stat = "identity") +
   labs(title='Average tempo', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")

p11 <- ggplot(genres, aes(music_genre, valence, fill = music_genre)) +     
  geom_bar(stat = "identity") +
   labs(title='Average valence', x = "Genre")+
  theme(axis.text = element_text(size = 3), axis.title = element_text(size = 5), plot.title = element_text(size = 10), legend.position="none") +
  scale_fill_brewer(palette = "PuOr")


p1 + p2 + p3 + p4 + p5 + p6 
p7 + p8 + p9 + p10 + p11
```

