---
title: "Music_PredictionEDA"
author: "Ange Olson"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
library(ezids)
```


Reading in the dataset: All come in as expected (date is a character, but we don't need this because it's not really realted to the song data)

```{r}
#setwd("/Users/angelinaolson/Desktop/GW/Intro DATS 6101")
music = data.frame(read.csv("music_genre.csv"))
```

How many genres are there? How many observations in each?

```{r, results = 'markup'}
library(dplyr)
genres <- music %>%
     group_by(music_genre) %>%
     count()
genres
```


What keys are present across what genres? For grins, chi-squared test?

```{r, results = 'markup'}
Cont_Table <- table(music$music_genre, music$key)
xkabledply(Cont_Table, title="Contingency Table for Genre and Key")
chitest = chisq.test(Cont_Table)
chitest
```

Results: different frequencies across genre!

Other than missing values (drop), perfectly balanced dataset.

```{r}
# drop those blank genre values 
music = music[!(music$music_genre == ""),]
```


ANOVA tests across genre: All stat sig!

```{r, results = 'markup'}
# convert tempo to numeric
music$tempo <- as.numeric(music$tempo)

# created some na values...let's see what

tempoNA <- music %>%
     group_by(is.na(music$tempo)) %>%
     count()
tempoNA
# not enough to cause concern 
```

```{r, results = 'markup'}
# simplify dataset 
musicNum <- music[, c(4:9, 11:12, 14:15, 17, 18)]

# run tests
library(tidyverse)
anova_results <- purrr::map(musicNum[,1:11], ~summary(aov(.x ~ musicNum$music_genre)))
anova_results
```